---
title: "index"
author: "Jaime Pulgar"
date: "6/6/2022"
output: 
  html_document:
    self_contained: false
---

## Dataset:
## "https://www.nytimes.com/interactive/2017/06/23/opinion/trumps-lies.html"

## Packages R for Web Scraping
## RCurl
## httr
## XML
## rvest

## Packages to process data
## xml2

## Other packages for data manipulation
## stringr
## dplyr
## lubridate
## readr
## knitr

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RCurl)
library(httr)
library(XML)
library(rvest)
library(xml2)
library(stringr)
library(dplyr)
library(lubridate)
library(readr)
library(knitr)

```

## Disable warnings
```{r echo=TRUE}
options(warn = -1)
```

## Reading from web page - returns xml document
```{r echo=TRUE}

webpage <- read_html("https://www.nytimes.com/interactive/2017/06/23/opinion/trumps-lies.html")
webpage

```

## Extracting records
```{r echo=TRUE}

results <- webpage %>% html_nodes(".short-desc")
results

```

## Building dataset
## We create an emthy list to receive the data that we will extract from the web page
```{r include=FALSE}

records <- vector("list", length = length(results))
records

```

## Extranting the data
```{r echo=TRUE}

for (i in seq_along(results)) { 
  date <- str_c(results[i] %>% 
                  html_nodes("strong") %>% 
                  html_text(trim = TRUE), ', 2017')  

  lie <- str_sub(xml_contents(results[i])[2] %>% html_text(trim = TRUE), 2, -2)
  

  explanation <- str_sub(results[i] %>% 
                           html_nodes(".short-truth") %>% 
                           html_text(trim = TRUE), 2, -2) 
  
  url <- results[i] %>% html_nodes("a") %>% html_attr("href")
  
  records[[i]] <- data_frame(date = date, lie = lie, explanation = explanation, url = url)
}

```

## Final dataset, bind_rows() function joins all rows of records object
```{r echo=TRUE}

df <- bind_rows(records)

```

## Transforming date field to Date format in R
```{r echo=TRUE}

df$date <- mdy(df$date)

```

## Exporting to CSV
```{r echo=TRUE}

write_csv(df, "lies_trump.csv")

```

## Reading the data
```{r echo=TRUE}

df <- read_csv("lies_trump.csv")
df %>% 
  kable(format = "html")

```
